---
title: "Possitional accuracy - RMSE Computation"
output: word_document
---

```{r, message=FALSE, warning=FALSE}
library(rgdal)
library(rgeos)
library(spdep)
library(sp)
library(plotKML)
library(plyr)
```
#Introduction

This is an algorithm that automatises the computation of RMSE between OSM road intersections and equivalent intersections digitised using Google Earth imagery.

**The inputs for this algorithm are:**

1. The admin units selected for the sampling process   
2. The road OSM intersections selected for the sampling process
3. Equivalent intersections digitized in Google Earth   

**The outputs of the algorithm are:**
 
1. RMSE at country level
2. RMSE for urban regions  
3. RMSE for rural regions  

```{r}
country_data_input <- "..."
```

Read and project input data

```{r}
setwd(country_data_input)
admin_units <- readOGR(country_data_input,'admin_units_tagged',verbose=FALSE)
admin_units_proj <- spTransform(admin_units, CRS("+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))
osm_data <- readOGR(country_data_input,'intersections_select',verbose=FALSE)
osm_data_proj <- spTransform(osm_data, CRS("+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))
ogrListLayers(dsn="sampled_intersections.kml") 
sampled_data <-readOGR(dsn="sampled_intersections.kml",layer="Temporary Places")
sampled_data_proj<- spTransform(sampled_data, CRS("+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))
sampled_data_proj <- intersect(sampled_data_proj, admin_units_proj)
sampled_data_proj <- sampled_data_proj[, c(1, 3,58)]
```

Match 

```{r}
sampled_data_proj@data$owncoordsX <- sampled_data_proj@coords[,1]
sampled_data_proj@data$owncoordsY <- sampled_data_proj@coords[,2]
osm_data_proj@data$matchcoordsX <- osm_data_proj@coords[,1]
osm_data_proj@data$matchcoordsY <- osm_data_proj@coords[,2]
sampled_data_analysis <- merge(sampled_data_proj,osm_data_proj,by="Name")
sampled_data_analysis@data$matchdist <- spDists(cbind(sampled_data_analysis@data$owncoordsX,sampled_data_analysis@data$owncoordsY),cbind(sampled_data_analysis@data$matchcoordsX,sampled_data_analysis@data$matchcoordsY),diagonal = TRUE)
sampled_data_analysis1 <- sampled_data_analysis[sampled_data_analysis@data$matchdist<300, ]
only_data<-sampled_data_analysis1@data
```

Compute RMSE statistics at country level

```{r}
freq=length(only_data$Name)
x_rmse <-sqrt( mean( (only_data$owncoordsX-only_data$matchcoordsX)^2, na.rm = TRUE) )
y_rmse <-sqrt( mean( (only_data$owncoordsY-only_data$matchcoordsY)^2, na.rm = TRUE) )
tot_rmse<-sqrt( mean( (only_data$owncoordsX-only_data$matchcoordsX)^2+(only_data$owncoordsY-only_data$matchcoordsY)^2 , na.rm = TRUE ))
rmse<-data.frame(Nr_Points=freq,X_Rmse=x_rmse,Y_Rmse=y_rmse,RMSE=tot_rmse)
rmse
```

Compute urban and rural RMSE statistics

```{r}
urban_rural<-ddply(only_data,"type",function(x){
freq=length(x$type)
x_rmse <-sqrt( mean( (x$owncoordsX-x$matchcoordsX)^2, na.rm = TRUE) )
y_rmse <-sqrt( mean( (x$owncoordsY-x$matchcoordsY)^2, na.rm = TRUE) )
tot_rmse<-sqrt( mean( (x$owncoordsX-x$matchcoordsX)^2+(x$owncoordsY-x$matchcoordsY)^2 , na.rm = TRUE ) )
data.frame(Nr_Points=freq,X_Rmse=x_rmse,Y_Rmse=y_rmse,RMSE=tot_rmse)})
urban_rural
```

Compute urban and rural RMSE statistics

```{r}
regional<-ddply(only_data,"UBID",function(x){
freq=length(x$UBID)
x_rmse <-sqrt( mean( (x$owncoordsX-x$matchcoordsX)^2, na.rm = TRUE) )
y_rmse <-sqrt( mean( (x$owncoordsY-x$matchcoordsY)^2, na.rm = TRUE) )
tot_rmse<-sqrt( mean( (x$owncoordsX-x$matchcoordsX)^2+(x$owncoordsY-x$matchcoordsY)^2 , na.rm = TRUE ) )
data.frame(Nr_Points=freq,X_Rmse=x_rmse,Y_Rmse=y_rmse,RMSE=tot_rmse)})
regional
sd(regional$RMSE)
```
