---
title: "Positional accuracy - Analysis of sampling methods"
output: html_document
---

#Introduction

This is a script that verifies the correlation between the number of versions of OSM road network features and positional accuracy. 
Road intersections were tagged with the average number of versions of 'parent' road segments. 
Also they were tagged with thier RMSE respective to coresponding intersection sampled on imagery.

**Inputs
1. The road OSM intersections selected for the sampling process tagged with the average number of version of parent roads
2. Equivalent intersections digitized in Google Earth 

**Outputs
1. Correlation statistics between average version numbers and RMSE 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
setwd("...")
source("basic_analysis.txt")
source("regional_analysis.txt")
source("urban_rural_analysis.txt")
source("match_data.txt")
source("sensitivity_analysis.txt")
source("sensitivity_analysis_correction.txt")
```

```{r, message=FALSE, warning=FALSE}

liberia_urban_rural_data_location <-'...'

guinea_urban_rural_data_location <- '...'

ghana_data_location <- '...'

senegal_data_location <- '...'
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(rgdal)
library(maptools)
library(raster)
library(rgeos)
library(classInt)
library(RColorBrewer)
library(RANN)
library(Matrix)
library(spdep)
library(plyr)
library(ggplot2)
library(gridExtra)
library(rmarkdown)
library(xtable)
library(Rlab)
```

## Versioning analysis

```{r, echo=FALSE, message=FALSE, warning=FALSE}

##Read/Prepare Liberia##
keeps <- c("Name","MEAN_osmve","pointRMSE","Type")
ge_data_urban_rural <- readOGR(liberia_urban_rural_data_location,'ge_data',verbose=FALSE)
osm_data_urban_rural <- readOGR(liberia_urban_rural_data_location,'osm_data',verbose=FALSE)
a<-match_data(ge_data_urban_rural,osm_data_urban_rural)
new_a <- a[,(names(a) %in% keeps)]


##Read/Prepare Guinea##

ge_data_urban_rural <- readOGR(guinea_urban_rural_data_location,'ge_data',verbose=FALSE)
osm_data_urban_rural <- readOGR(guinea_urban_rural_data_location,'osm_data',verbose=FALSE)
b<-match_data(ge_data_urban_rural,osm_data_urban_rural)
new_b <- b[,(names(b) %in% keeps)]

##Read/Prepare Ghana##
setwd(ghana_data_location)
admin_units <- readOGR(ghana_data_location,'admin_units_tagged',verbose=FALSE)
admin_units_proj <- spTransform(admin_units, CRS("+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))
osm_data_urban_rural <- readOGR(ghana_data_location,'intersections_select',verbose=FALSE)
ge_data_urban_rural <-readOGR(dsn="sampled_intersections.kml",layer="Temporary Places")
ge_data_urban_rural<-spTransform(ge_data_urban_rural, CRS("+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))
osm_data_urban_rural <- intersect(osm_data_urban_rural, admin_units_proj)
colnames(osm_data_urban_rural@data)[60] <- "Type"
c<-match_data(ge_data_urban_rural,osm_data_urban_rural)
new_c <- c[,(names(c) %in% keeps)]

##Read/Prepare Senegal##

setwd(senegal_data_location)
admin_units <- readOGR(senegal_data_location,'admin_units_tagged',verbose=FALSE)
admin_units_proj <- spTransform(admin_units, CRS("+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))
osm_data_urban_rural <- readOGR(senegal_data_location,'intersections_select',verbose=FALSE)
ge_data_urban_rural <-readOGR(dsn="sampled_intersections.kml",layer="Temporary Places")
ge_data_urban_rural<-spTransform(ge_data_urban_rural, CRS("+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))
osm_data_urban_rural <- intersect(osm_data_urban_rural, admin_units_proj)
colnames(osm_data_urban_rural@data)[60] <- "Type"
d<-match_data(ge_data_urban_rural,osm_data_urban_rural)
new_d <- d[,(names(d) %in% keeps)]
```

```{r, include=FALSE}
countries = c("Liberia", "Guinea", "Ghana", "Senegal","Global-U","Global-R","Global-U-R") 
coeff_all_values = c(0, 0, 0, 0, 0, 0, 0)
all_count = c(0, 0, 0, 0, 0, 0, 0)
coeff_subset = c(0, 0, 0, 0, 0, 0, 0) 
subset_count = c(0, 0, 0, 0, 0, 0, 0)
correlation = data.frame(countries, coeff_all_values, all_count, coeff_subset, subset_count)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Liberia

analysis_data <- new_a
correlation$coeff_all_values[1] <- cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[1] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[1] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[1]<- length(analysis_data_filtered@data$MEAN_osmve)

#Guinea

analysis_data <- new_b
correlation$coeff_all_values[2] <- cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[2] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[2] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[2]<- length(analysis_data_filtered@data$MEAN_osmve)

#Ghana

analysis_data <- new_c
correlation$coeff_all_values[3] <-cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[3] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[3] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[3]<- length(analysis_data_filtered@data$MEAN_osmve)

#Senegal

analysis_data <- new_d
correlation$coeff_all_values[4] <- cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[4] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[4] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[4]<- length(analysis_data_filtered@data$MEAN_osmve)

#Global - Urban Data Only

analysis_data <- rbind(new_a,new_b,new_c,new_d)
analysis_data <- analysis_data[analysis_data@data$Type=="urban",]
correlation$coeff_all_values[5] <- cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[5] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[5] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[5]<- length(analysis_data_filtered@data$MEAN_osmve)

#Global - Rural Data Only

analysis_data <- rbind(new_a,new_b,new_c,new_d)
analysis_data <- analysis_data[analysis_data@data$Type=="rural",]
correlation$coeff_all_values[6] <- cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[6] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[6] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[6]<- length(analysis_data_filtered@data$MEAN_osmve)

#Global - Urban - Rurla Data

analysis_data <- rbind(new_a,new_b,new_c,new_d)
correlation$coeff_all_values[7] <- cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[7] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[7] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[7]<- length(analysis_data_filtered@data$MEAN_osmve)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
setwd("...")
write.table(correlation, file = "foo.csv", sep = ",")
analysis_data <- rbind(new_a,new_b,new_c,new_d)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve<=10,]
png('versioning_correlation.png',width = 10, height= 7, units = 'in' , res = 300)
ggplot(analysis_data_filtered@data,aes(MEAN_osmve,pointRMSE))+geom_point(color="blue")+xlab("Number of versions (-)") + ylab("RMSE (m)")+xlim(0, 10)+geom_smooth(data=analysis_data@data,aes(MEAN_osmve,pointRMSE),method=lm,se=FALSE)
dev.off()
```